PhD Thesis

### 2017-01-17 aosd13/pepm13/caseStudyDiscussion.tex
More rearranging

In this section we discuss the degree to which \LoS\ fulfilled our original design goals, and the conclusions
for host and domain-specific language design.

\subsection{What worked well}
Several features of Scala contributed greatly to the success we achieved. With implicit conversions, the lifting can be made mostly transparent. The advanced type system features were quite helpful to make the expression tree representation typed. The fact that for-comprehensions are desugared \emph{before} type inference and type checking was also a prerequisite for automatic lifting. The syntactic expressiveness and uniformity of Scala, in particular the fact that custom types can have the same look-and-feel as primitive types, were also vital to lift expressions on primitive types.

>>>>

In this chapter we discuss the degree to which \LoS\ fulfilled our original design goals, and the conclusions
for host and domain-specific language design.

\section{Deep embedding}
\subsection{What worked well}
Several features of Scala contributed greatly to the success we achieved. With implicit conversions, the lifting can be made mostly transparent. The advanced type system features were quite helpful to make the expression tree representation typed. The fact that for-comprehensions are desugared \emph{before} type inference and type checking was also a prerequisite for automatic lifting. The syntactic expressiveness and uniformity of Scala, in particular the fact that custom types can have the same look-and-feel as primitive types, were also vital to lift expressions on primitive types.
